%====================
% EXPERIENCE A
%====================

\subsection{{"Tilde" Compiler \hfill January 2023 --- May 2023}}
\subtext{University of Missouri - St. Louis \hfill St. Louis, MO}
\begin{zitemize}
\item Developed a compiler with the goal of compiling a rudimentary programming language nicknamed "Tilde" into assembly code.
\item Created an intuitive command line interface allowing for multiple methods of code input.
\item Implemented a lexer, LL parser, and variable static semantics as well as a Visual Studio Code plugin to allow for syntax highlighting.
\item Tutored peers in concepts related to the compiler as well as providing programming and debug assistance.
\end{zitemize}

%====================
% EXPERIENCE B
%====================

\subsection{{"We are St. Louis" Interactive Map \hfill October 2022 --- December 2022}}
\subtext{University of Missouri - St. Louis \hfill St. Louis, MO}
\begin{zitemize}
\item Co-led a team in the design and development of a web-based interactive public history and storytelling project.
\item Utilized agile methodology and adjusted design during development based on customer feedback.
\item Developed a salted hash-based secure authentication system for website administrators.
\item Integrated technologies such as JavaScript, MySQL, PHP, and Apache in a full stack web development role.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
