%====================
% WORK A
%====================

\subsection{{Web Developer \hfill February 2023 --- Present}}
\subtext{We Are St. Louis \hfill St. Louis, MO}
\begin{zitemize}
\item Developed and updated the website of a non-profit organization based at the University of Missouri - St. Louis.
\item Integrated ArcGIS Web, Wordpress, and Omeka S technologies to create a cohesive user experience site-wide.
\item Created custom plugins to add features to existing technology that lacked required functionality.
\item Worked independently and remotely while meeting deadlines and maintaining communication with organization staff.
\end{zitemize}

%====================
% WORK B
%====================
\subsection{{Sales and Customer Service Representative  \hfill April 2021 --- Present}}
\subtext{Waldbart Nursery \hfill St. Louis, MO}
\begin{zitemize}  
\item Worked directly with contractors and retail customers to meet landscaping needs and finalize sales.
\item Performed maintenance on and operated farm machinery in a self-supervised environment.
\item Effectively communicated and cooperated with coworkers to complete large scale projects and orders.
\item Managed IT duties and support for the Florissant nursery location.
\end{zitemize}

%====================
% WORK C
%====================

\subsection{{Resident Assistant \hfill March 2020 --- December 2020}}
\subtext{Valparaiso University \hfill Valparaiso, IN}
\begin{zitemize}
\item Worked to help orient residents to campus life, connecting with each student weekly.
\item Organized events and activities for residents to facilitate interaction outside the classroom and foster community.
\end{zitemize}

%====================
% WORK D
%====================

\subsection{{Hesse Scholar Tutor \hfill August 2018 --- December 2019}}
\subtext{Valparaiso University \hfill Valparaiso, IN}
\begin{zitemize}
\item Provided walk-in peer tutoring and help sessions for STEM students in first and second year classes.
\end{zitemize}